Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-04 paper/ijm.tex
Update ijm.tex
Small correction eq 1 chapter 4. \ added
Update ijm.tex
Changed text p.13

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: alpha^{g}{}' X_{it}^{g} + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_{t}^{g} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y_{it}^{g}$ is the outcome (either unemployment indicator
or logarithm of net monthly wage)
of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
characteristics for both groups; $L$ is the vector of
language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code. I found the code for estimations with these interactions, but I don't remember that I used these interactions for the tables.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

@@

We estimate the effect of language skills for unemployment as well for the second model. However too little results are statistically significant. The importance of Estonian language skills was growing during the latest periods and is associated with approximately 7 percentage points lower unemployment for both Russian men and women. The best results are reached for the youngest age groups and for middle age groups.
English skills are related to less unemployment both for Russian men and women. The effect is smaller for Estonian men while for Estonian women all results are insignificant.

>>>>

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: \alpha^{g}{}' X_{it}^{g} + \vec{\beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_{t}^{g} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y_{it}^{g}$ is the outcome (either unemployment indicator
or logarithm of net monthly wage)
of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
characteristics for both groups; $L$ is the vector of
language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code. I found the code for estimations with these interactions, but I don't remember that I used these interactions for the tables.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

@@

We estimate the effect of language skills for unemployment for the age groups and ethnical groups as well for the second model. However dividing the results for four sub-periods does not detect the trends across the age groups for those periods due to only some of the results are statistically significant. The exception is the group of young (25-34) Estonian men for whom English language is clearly decreases the probability of being unemployment during the time. Notwithstanding importance of English is small for other groups.
Estimates for the longer time period shows the importance of Estonian language for all age groups for ethnical Russian and have even higher impact for the young women.
